Spatial Analysis

### 2021-11-11 Scripts/spatial_analisis.Rmd
included new grid data with selected fishing ports

@@

grids <- bind_rows(
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Paralichthys dentatus"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Stenotomus chrysops"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Centropristis striata")
) %>% 
  mutate(spatial = "sw") %>% 
  bind_rows(
    my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T)
  ) %>% 
  mutate(spatial = ifelse(is.na(spatial),"fp",spatial),
         spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
                 ifelse(spp == "scup", "Stenotomus chrysops", 
                        "Centropristis striata"
                 )
    )
  ) %>% 
  distinct(.keep_all = T)

@@

# Ports data
ports_df <- my_path("R","Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th") %>%
  distinct(port_name, .keep_all = T) # No need for duplication

@@

# The plot
map_plot <- land_sf %>% 
  left_join(reg_unit,
            by = "state") %>% 
  filter(spatial != "Difference") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
                              breaks = seq(0,35,5),
                              limits=(c(0,35))
                              )+
  facet_grid(spatial~ spp+label) +
  labs(x = "", 
       y = "") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"))

diff_plot <- land_sf %>% 
  left_join(reg_unit,
            by = "state") %>% 
  filter(spatial == "Difference") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
                              breaks = seq(0,20,5),
                              limits=(c(0,22)),
                              # labels = c("<-10",seq(-75,75,25),">100")
                              ) +
  facet_grid(spatial~ spp+label) +
  labs(x = "", 
       y = "") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"),
        strip.background = element_blank(),
        strip.text.x = element_blank()
        )

@@

reg_unit %>% 
  # filter(spatial == "fp") %>%
  select(-fp) %>% 
  spread(label,sw) %>% 
  mutate(
    difference = Today-Reference
    ) %>% 
  gther(Reference:difference)

>>>>

x <- as.data.frame(st_read(my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))) %>% 
  select(index,spp = spcs_nm,port_name = port_nm, abrev = stt_pst) %>% 
  bind_cols(
    as.data.frame(st_coordinates(st_read(my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))))
  ) %>% 
  rename(lon = X, lat = Y) %>% 
  left_join(as.data.frame(land_sf),
            by = "abrev") %>% 
  mutate(state= str_to_sentence(ID)) %>% 
  select(1:6,state) %>% 
  mutate(
     spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
                 ifelse(spp == "scup", "Stenotomus chrysops", 
                        "Centropristis striata"
                 )
    )
  )

write_csv(x,my_path("D", "Partial/grid_fp",name="grid_eez_fp_df.csv"))

@@

grids_sw <- bind_rows(
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Paralichthys dentatus"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Stenotomus chrysops"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Centropristis striata")
) %>% 
  mutate(spatial = "sw",
         port_name = NA,
         abrev = NA
         )

grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
) %>%
  mutate(spatial = "fp")

# Join both approaches
grids <- bind_rows(grids_sw,grids_fp)

@@

# Ports data
ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th") %>%
  distinct(port_name, .keep_all = T) # No need for duplication

@@

# The plot
map_plot <- land_sf %>% 
  left_join(reg_unit,
            by = "state") %>% 
  filter(spatial != "Difference") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
                              breaks = seq(0,55,5),
                              limits=(c(0,55))
                              )+
  facet_grid(spatial~ spp+label) +
  labs(x = "", 
       y = "") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"))

diff_plot <- land_sf %>% 
  left_join(reg_unit,
            by = "state") %>% 
  filter(spatial == "Difference") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
                              breaks = seq(0,45,5),
                              limits=(c(0,45)),
                              # labels = c("<-10",seq(-75,75,25),">100")
                              ) +
  facet_grid(spatial~ spp+label) +
  labs(x = "", 
       y = "") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"),
        strip.background = element_blank(),
        strip.text.x = element_blank()
        )

@@
